Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-05 paper/preprint/appendix.Rmd

# Discontinuity Analysis

We next examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the amount of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
[table with each child's age of onset per milestone?]

@@

>>>>

# Motor Milestones Analysis

We next examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
We tried including random slopes by age and milestone, but the models did not converge and/or were singular.
Thus, for each milestone the R syntax was: \texttt{prop_faces ~ age * milestone + (1 | child_id)}.

Children's age of achieving each milestone was dummy-coded (i.e., 0=milestone not reached; 1=milestone reached).
Participants S and A were already able to sit at 6 months of age, while Y began achieving this milestone at 8 months.
A was able to cruise at 9 months of age, while S reached that milestone at 10 months, with Y just behind.
Learning to walk showed the most variation, with S walking after 10 months, A after 13 months, and Y after 16 months of age.

@@

face_all <- lmer(prop_faces ~ age * (sit + cruise + walk) + (1 | child_id), 
     data=face_hand_by_age_milestones) 
#summary(face_all) # cruise+ age:cruise-

hand_all <- lmer(prop_hands ~ age * (sit + cruise + walk) + (1 | child_id), 
     data=face_hand_by_age_milestones) 
#summary(hand_all) # cruise+ age:cruise-.

### 2022-01-05 paper/preprint/manuscript_dec2021_apa_blinded.Rmd

Second, we also found an unexpectedly high proportion of hands in infants' view, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work. 
Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. 
During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations and between individual children. Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. Each of these positions offer the child differing degrees of visual access to faces and hands. While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.

>>>>

Second, we also found an unexpectedly high proportion of hands in infants' view, even when restricting the analysis to detections in the center field-of-view to make the viewpoints comparable to those of headcams used in prior work. 
Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. 
During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). 
Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. 
Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations (see Appendix, Figure S7?) and between individual children. 
Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. 
This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. 
Each of these positions offer the child differing degrees of visual access to faces and hands. 
While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.
